Articles of Association of London Hackspace Ltd

### 2014-09-13 constitution/articles-body.tex
Add missing tag
Increase maximum size of the board to 9
Initial provision for electronic elections

\item
  \begin{enumerate}
  \item
    A director must be a natural person aged 16 years or older.
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article
    \ref{director-cease}.
  \item
    The number of directors shall be not less than three, nor more than eight.

@@

\section{Retirement of Directors}

\item
    At the first annual general meeting all the directors must retire from
    office unless by the close of the meeting the members have failed to
    elect sufficient directors to hold a quorate meeting of the directors. At
    each subsequent annual general meeting one-third of the directors or, if
    their number is not three or a multiple of three, the number nearest to
    one-third, must retire from office. If there is only one director he or she
    must retire.

@@

\item
  \begin{enumerate}
  \item \label{dissolve-transfer}
    The members of the association may at any time before, and in
    expectation of, its dissolution resolve that any net assets of the
    association after all its debts and liabilities have been paid, or
    provision has been made for them, shall on or before the
    dissolution of the association be applied or transferred in any of the
    following ways:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any association for purposes similar to the
      Objects; or
    \item
      to any association for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    Subject to any such resolution of the members of the association, the
    directors of the association may at any time before and in expectation
    of its dissolution resolve that any net assets of the association after
    all its debts and liabilities have been paid, or provision made for
    them, shall on or before dissolution of the association be applied or
    transferred:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any association for purposes similar to the
      Objects; or
    \item
      to any association for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    In no circumstances shall the net assets of the association be paid to
    or distributed among the members of the association (except to a member
    that is itself a association) and if no resolution in accordance with
    article \ref{dissolve-transfer} is passed by the members or the directors the net
    assets of the association shall be applied for charitable purposes as
    directed by the Court or the Commission.
  \end{enumerate}

>>>>

\item
  \begin{enumerate}
  \item
    A director must be a natural person aged 16 years or older.
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article
    \ref{director-cease}.
  \item
    The number of directors shall be not less than three, nor more than nine.

@@

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method with a "no further places" candidate must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item Directors standing for re-election will remain directors until the successful conclusion
          of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
   \end{enumerate}

\section{Retirement of Directors}
\item
    \begin{enumerate}
        \item At the first directors election, all the directors must retire from office unless the election
              fails to elect sufficient directors to hold a quorate meeting of the directors.
        \item At each subsequent directors election, one-third of the directors or, if their number is
              not three or a multiple of three, the number nearest to one-third, must retire from office.
              If there is only one director, they must retire.
        \item The directors to retire by rotation shall be those who have been longest in office since their
              last appointment. If any directors became or were appointed directors
              on the same day, those to retire shall (unless they otherwise agree among themselves)
              be determined by lot.
        \item Retiring directors may stand for re-election.
    \end{enumerate}

@@

\item
  \begin{enumerate}
  \item \label{dissolve-transfer}
    The members of the association may at any time before, and in
    expectation of, its dissolution resolve that any net assets of the
    association after all its debts and liabilities have been paid, or
    provision has been made for them, shall on or before the
    dissolution of the association be applied or transferred in any of the
    following ways:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any association for purposes similar to the
      Objects; or
    \item
      to any association for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    Subject to any such resolution of the members of the association, the
    directors of the association may at any time before and in expectation
    of its dissolution resolve that any net assets of the association after
    all its debts and liabilities have been paid, or provision made for
    them, shall on or before dissolution of the association be applied or
    transferred:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any association for purposes similar to the
      Objects; or
    \item
      to any association for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    In no circumstances shall the net assets of the association be paid to
    or distributed among the members of the association (except to a member
    that is itself a association) and if no resolution in accordance with
    article \ref{dissolve-transfer} is passed by the members or the directors the net
    assets of the association shall be applied for charitable purposes as
    directed by the Court.
  \end{enumerate}
\end{enumerate}
